# Feedback

There are several ways to implement feedback in PsychoPy for stimulus-response experiments. What they have in common is that they all assume that the `response.corr` variable is available.

One style is to present the participant with text indicating whether they respond correctly or not for each trial.

Within that style there is more than one way to implement the feedback in PsychoPy.

## Per-trial method 1

One way is to insert a feedback Routine after the Trial Routine that contains a single Text Component whose contents and colour are set to variables  whose values we calculate using a Code component, based on the value of `response.corr`. See @fig-fbackmethod1 for a screencast of writing this method., and see @fig-fbackmethod1runtime for the runtime. This is file5.psyexp.
```{r}
#| echo: false
#| label: fig-fbackmethod1
#| fig-cap: Feedback using a single text component and passing variables in for text content and text colour
htmltools::tags$video(src = "obs/2022-07-03 03-43-24.mkv", type = "video/mp4", width="100%", controls=1)
```

```{r}
#| echo: false
#| label: fig-fbackmethod1runtime
#| fig-cap: Feedback using a single text component and passing variables in for text content and text colour (runtime)
htmltools::tags$video(src = "obs/2022-07-03 03-52-45.mkv", type = "video/mp4", width="100%", controls=1)
```

## Per-trial Method 2

Another way is to insert the Feedback Routine after the Trial Routine, in the same way, but this time to create a Text component for each of the possible outcomes of the trial - normally _correct_ and _incorrect_ but also sometimes _time-out_. We then select one single outcome to display with reference to the value of `response.corr`. This is file6.psyexp.

```{r}
#| echo: false
#| label: fig-fbackmethod2
#| fig-cap: Feedback using multiple text components, one for each outcome, with fixed content and colour, and then supplying as the `Start` value not a time but a condition
htmltools::tags$video(src = "obs/2022-07-03 04-17-38.mkv", type = "video/mp4", width="100%", controls=1)
```

```{r}
#| echo: false
#| label: fig-fbackmethod2runtime
#| fig-cap: Feedback using multiple text components, one for each outcome, with fixed content and colour, and then supplying as the `Start` value not a time but a condition (runtime)
htmltools::tags$video(src = "obs/2022-07-03 04-21-17.mkv", type = "video/mp4", width="100%", controls=1)
```



## Average RT and accuracy

file7.psyexp includes a screen at the end of each trial that presents the cumulative mean RT and mean accuracy.

the code for this is part of the `evaluate_response` component that we used in method one of providing feedback, where we had a single feedback component and used variables to decide what it should show.

```{python}
#| echo: true
#| eval: false
if response.keys:
    if response.corr==1:
        sum_ac=sum_ac+1
        sum_rt=sum_rt+response.rt
        feedback_colour="green"
        feedback_text="CORRECT!"
    if response.corr==0:
        sum_rt=sum_rt+response.rt
        feedback_colour="red"
        feedback_text="Wrong!"
else:
    sum_rt=sum_rt+2.0
    feedback_colour="black"
    feedback_text="Timed out - please respond faster!"
mean_ac=sum_ac/(trials.thisTrialN+1)
mean_rt=sum_rt/(trials.thisTrialN+1)

```

