# Finessing the Trial Loop

At this stage things are basically working - the trial sequence is being randomised correctly; the images come up for the right amount of time; etc.

However we can improve some things quite easily going into the `file3.psyexp`

* add an inter-trial interval (0.5 seconds)
* set the images to be prepared during the inter-trial interval (better stimulus duration consistency)
* give the components names that will help us understand better what they do when we see them later in results files
* make the stimulus duration longer (the images were going by without responses because the duration was too short) - try 1.5 seconds.

@fig-finesseTrialLoop shows how to do this finessing.

```{r}
#| echo: false
#| label: fig-finesseTrialLoop
#| fig-cap: Finessing the trial loop
htmltools::tags$video(src = "obs/2022-07-03 01-38-39.mkv", type = "video/mp4", width="100%", controls=1)
```

@fig-finesseTrialLoopRunTime shows the runtime now after a little finessing.

```{r}
#| echo: false
#| label: fig-finesseTrialLoopRunTime
#| fig-cap: Finessing the trial loop - runtime
htmltools::tags$video(src = "obs/2022-07-03 02-01-24.mkv", type = "video/mp4", width="100%", controls=1)
```

:::{.callout-note}
## Download
Click [file3](psy/file3.zip) to download the file3 psyexp as it stands after a little finessing.
:::
