# Making the trial loop

See @{fig-mkTrialLoop} for:

* add trials Routine
  * add image
    * set duration (1.0 seconds)
    * use `$animal_image` for `image.Image` field and change drop-down from _constant_ to _set every repeat_
  * add keyboard
    * set allowed_keys field to `'c','d'`
    * set duration to 1.0 seconds - now they won't be able to respond after the image disappears. The keyboard's start and stop times are the same as the image's
  * enclose with loop
    * The `Conditions` field is where you put the name of the spreadsheet
    * leave 'random' - the default - but notice that sequential is also available
    * change the default from 5 to 1 (because we only want to run the ten trials once)

```{r}
#| echo: false
#| label: fig-mkTrialLoop
#| fig-cap: Making the trial loop
htmltools::tags$video(src = "obs/addTrialsLoop.mp4", type = "video/mp4", width="100%", controls=1)
```

See @fig-runTrialLoop for the runtime as things stand now.

```{r}
#| echo: false
#| label: fig-runTrialLoop
#| fig-cap: Running the basic loop
htmltools::tags$video(src = "obs/2022-07-03 01-27-54.mkv", type = "video/mp4", width="100%", controls=1)
```

:::{.callout-note}
## Download
Click [file2](psy/file2.zip) to download the psyexp in a crude but working state.
:::
